---
title: "EMPI Check"
output:
  html_document:
    toc: yes
    runtime: shiny
---

<!Define CSS> 
<style>
body, td {
   font-family: sans-serif;
   background-color: white;
   font-size: 10px;
   margin: 8px;
}

tt, code, pre {
   font-family: 'DejaVu Sans Mono', 'Droid Sans Mono', 'Lucida Console', Consolas, Monaco, monospace;
}

h1 { 
   font-size:2.2em; 
}

h2 { 
   font-size:1.8em; 
}

h3 { 
   font-size:1.4em; 
}

h4 { 
   font-size:1.0em; 
}

h5 { 
   font-size:0.9em; 
}

h6 { 
   font-size:0.8em; 
}

a:visited {
   color: rgb(50%, 0%, 50%);
}

pre {  
   margin-top: 0;
   max-width: 95%;
   border: 1px solid #ccc;
   white-space: pre-wrap;
}

pre code {
   display: block; padding: 0.5em;
}

code.r, code.cpp {
   background-color: #F8F8F8;
}

/*
  Web20 Table Style
  written by Netway Media, http://www.netway-media.com
*/
table {
  border-collapse: collapse;
  border: 1px solid #666666;
  font: normal 11px verdana, arial, helvetica, sans-serif;
  color: #363636;
  background: #f6f6f6;
  text-align: right;
  width: auto;
  align: left;
  margin: auto;
  }
  
caption {
  text-align: center;
  font: bold 10px arial, helvetica, sans-serif;
  background: transparent;
  padding:6px 4px 8px 0px;
  color: #000000;
  text-transform: uppercase;
}

thead, tfoot {
background:url(bg1.png) repeat-x;
text-align:left;
height:30px;
}

thead th, tfoot th {
padding:5px;
}

table a {
color: #333333;
text-decoration:none;
}

table a:hover {
text-decoration:underline;
}

tr.odd {
background: #f1f1f1;
}

tbody th, tbody td {
padding:5px;
}

blockquote {
   color:#666666;
   margin:0;
   padding-left: 1em;
   border-left: 0.5em #EEE solid;
}

hr {
   height: 0px;
   border-bottom: none;
   border-top-width: thin;
   border-top-style: dotted;
   border-top-color: #999999;
}

@media print {
   * { 
      background: transparent !important; 
      color: black !important; 
      filter:none !important; 
      -ms-filter: none !important; 
   }

   body { 
      font-size:10pt; 
      max-width:100%; 
   }
       
   a, a:visited { 
      text-decoration: underline; 
   }

   hr { 
      visibility: hidden;
      page-break-before: always;
   }

   pre, blockquote { 
      padding-right: 1em; 
      page-break-inside: avoid; 
   }

   tr, img { 
      page-break-inside: avoid; 
   }

   img { 
      max-width: 100% !important; 
   }

   @page :left { 
      margin: 15mm 20mm 15mm 10mm; 
   }
     
   @page :right { 
      margin: 15mm 10mm 15mm 20mm; 
   }

   p, h2, h3 { 
      orphans: 3; widows: 3;
   }

   h2, h3 { 
      page-break-after: avoid;
   }
}
h1 {color:black; font-family:"Georgia"}
h2 {color:#dd6628}
h3 {color:#3a98cd}
p {color:black; text-align:justify;}

//
// Modal
// ----------------------

.modal{
  
   
  // This is modal bg
  &:before{
    content: ""; 
    display: none;
    background: rgba(0,0,0,.6);
    position: fixed;
    top: 0; left: 0; right: 0; bottom: 0; 
    z-index: 10;
  }
  
  &:target{
     
    // Active animate in modal
    &:before{
      display: block;
    }  
    .modal-dialog{
      .translate(0, 0); 
      top: 20%;  
    }
     
  }
  
}

// Modal Dialog
// ----------------------

.modal-dialog{
  background: #fefefe;
  border: @gray solid 1px;
  border-radius: 5px;
  margin-left: -200px;
  position: fixed; 
  left: 50%; 
  top: -100%;  
  z-index: 11; 
  width: 360px;
  .translate(0, -500%);
  .transition-transform(~"0.3s ease-out");
}

.modal-body{
  padding: @space/2;
}

.modal-header,
.modal-footer{
  padding: @space/4 @space/2;
}

.modal-header{
  border-bottom: @gray-lighter solid 1px;
  
  h2{
    font-size: 20px;
  }
  
}

.modal-footer{
  border-top: @gray-lighter solid 1px;
  text-align: right;
}


#close {
  display: none; 
}

</style>


<!Define CSS> 
```{r include=FALSE, cache=FALSE}
# if (!requireNamespace('htmlwidgets') || packageVersion('htmlwidgets') <= '0.3.2')
#   devtools::install_github('ramnathv/htmlwidgets')
# # install DT
# if (!require("DT")) devtools::install_github("rstudio/DT")
# # if (!require("purrr")) devtools::install_github("hadley/purrr")
# 
# #library(XLConnect)
# library(RODBC)
# library(data.table)
# library(sqldf)
# library(tidyr)
# library (plyr)
# library(dplyr)
# library(knitr)
# library(pander)
# library(purrr)
# library(ggplot2)
# library(chron)
# library(date)
# library(zoo)
# library(lubridate)
# library(reshape)
# library(shiny)
# library(shinyBS)
# library(DT)

##get common functions
# wd <-getwd()
# setwd('..')
# source('./SharedDataScripts/CommonFunctions.R')
# setwd(wd)
# remove(wd)
```

```{r include=FALSE, cache=FALSE}

##iPaaS
# IEnv <-"Stage"
# IDNS <- "IPAAS"
# IClient <- "CHS"
# IClientDB <-IDNS
# Entity <- 55
# 
# 
# ##ODS
# OEnv <-"UAT 01"
# ODNS <- "ODS"
# OClient <- "CHS"
# OClienntODS <-paste(OClient, ODNS, sep="")
# OClientDB <-paste(OClient, ODNS, sep="")
# Client <- 9

OClient <- CLIENTS %>%
  filter(Abbrev == input$clientInput) %>%
  select(Abbrev) %>%
  unique()

OClientDB <-paste(OClient, "ODS", sep="")

ClientID <- CLIENTS %>%
  filter(Abbrev == input$clientInput) %>%
  select(ClientID) %>%
  unique()

ODSAddress <- SERVERS %>%
  filter(Type == "ODS") %>%
  filter(Name == input$odsenvInput) %>%
  select(Path) %>%
  unique()

IPAASAddress <<- SERVERS %>%
  filter(Type == "IPAAS") %>%
  filter(Name == input$ipaasenvInput) %>%
  select(Path) %>%
  unique()

EntityID <- ENTITIES() %>%
  filter(ENTITY_NM == input$entityInput) %>%
  select(ENTITY_ID) %>%
  unique()

IEntity <- ENTITIES() %>%
  filter(ENTITY_NM == input$entityInput) %>%
  select(ENTITY_NM) %>%
  unique()

ODSEnv <- SERVERS %>%
  filter(Type == "ODS") %>%
  filter(Name == input$odsenvInput) %>%
  select(Name) %>%
  unique()

IPAASEnv <<- SERVERS %>%
  filter(Type == "IPAAS") %>%
  filter(Name == input$ipaasenvInput) %>%
  select(Name) %>%
  unique()


#get data
# setwd('./DataLoadScripts/')
source('GetEMPIData.R', local=TRUE)
# setwd('.')
# odbcCloseAll()
```
# Parameters
<ul class="list-group">
  <li class="list-group-item">ODS Client Evaluated:  `r OClient`</li>
  <li class="list-group-item">iPaaS Entity Evaluated: `r IEntity`</li>
  <li class="list-group-item">ODS Environment: `r ODSEnv`</li>
  <li class="list-group-item">iPaaS Environment: `r IPAASEnv`</li>
  <li class="list-group-item">ODS Server: `r ODSAddress`</li>
  <li class="list-group-item">iPaaS Server: `r IPAASAddress`</li>
</ul>



#iPaaS to ODS EMPI & MBR_ID Matches
<div class="panel panel-primary">
  <div class="panel-heading">Summary of records matching on EMPI and MBR_ID</div>
  <div class="panel-body">* For CONTROL_ID = 2, member match is made on client provided MBR_ID. 
  * A low match percentage indicates that EMPIs are out of sync between iPaaS and ODS.
  
```{r child = './tblEMPI_MBR_IDMatchSummary_1.Rmd'}
```


  </div>
</div>


#iPaaS to ODS EMPI & SYS_MBR_SK Matches
<div class="panel panel-primary">
  <div class="panel-heading">Summary of records matching on EMPI and SYS_MBR_SK </div>
  <div class="panel-body">* General check of EMPIs and SKs between iPaaS and ODS.
  * A low match percentage indicates that EMPIs are out of sync between iPaaS and ODS.
  
```{r child = './tblEMPI_SKMatchSummary_1.Rmd'}
```


  </div>
</div>


#iPaaS to ODS EMPI & Demographic Matches
<div class="panel panel-primary">
  <div class="panel-heading">Summary of records matching on EMPI and Demographic fields </div>
  <div class="panel-body">* For CONTROL_ID = 0, member match is made based on EMR demographic information.
  * A low match percentage indicates that the EMPIs are out of sync between iPaaS and ODS.
  
```{r child = './tblEMPI_DemographicsMatchSummary_1.Rmd'}
```


  </div>
</div>


#iPaaS to ODS SYS_MBR_SK & Demographic Matches
<div class="panel panel-primary">
  <div class="panel-heading">Summary of records matching on SYS_MBR_SK and Demographic fields </div>
  <div class="panel-body">* General check of SKs between iPaaS and ODS.
  * A low match percentage indicates that SKs are out of sync between iPaaS and ODS.
  
```{r child = './tblSK_DemographicsMatchSummary_1.Rmd'}
```


  </div>
</div>







